Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-30 PAPER.tex
edited signal loss definition

A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Additionally, accurate error estimation is crucial for the comparison of results to theoretical models. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for 21\,cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

>>>>

A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target \textit{cosmological} signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Additionally, accurate error estimation is crucial for the comparison of results to theoretical models. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for 21\,cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}
